\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}{\Large\bfseries}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[---]

\begin{document}

\begin{center}
    \textbf{\LARGE Aditya Kulkarni} \\[4pt]
    \href{mailto:adityark2603@gmail.com}{adityark2603@gmail.com} ~|~ +91 95383 74684 ~|~ \href{https://www.linkedin.com/in/adityark2603}{linkedin.com/in/adityark2603}
\end{center}

\section*{Education}
\textbf{PES University}, Bengaluru, Karnataka \
B.Tech in Electronics \& Communication \hfill Expected Sep 2027 \\
Concentration: Analog Circuit Design, Cadence Virtuoso Software \\
CGPA: 7.21 / 10 \\
Relevant Coursework: Statistics \& Probability, Linear Algebra, Signals \& Systems, Digital Circuit Design, Image Processing, DSP, Control Systems

\section*{Projects}
\textbf{Food Delivery Time Prediction Model} \\
\begin{itemize}[leftmargin=*]
    \item Developed ML models using location, traffic, weather, and personnel experience to predict delivery times.
    \item Achieved R\textsuperscript{2}: 0.80--0.90 (Linear Regression), Accuracy: 75--85\% (Logistic Regression).
    \item Provided insights for routing, staffing, and weather-based adjustments to improve delivery efficiency.
\end{itemize}

\textbf{Band-Gap Reference Circuit} \\
\begin{itemize}[leftmargin=*]
    \item Designed a BGR in Cadence combining PTAT and CTAT voltages to create temperature-independent output.
    \item Used current mirrors to stabilize output voltage between 1.29V and 1.33V across -50\textdegree C to 125\textdegree C.
\end{itemize}

\section*{Experience}
\textbf{Rotaract District 3191}, Bengaluru \\
\textit{Director of Community Services} \hfill Oct 2024 -- Present \\
\begin{itemize}[leftmargin=*]
    \item Led initiatives focusing on education, health, and environmental sustainability in local communities.
\end{itemize}

\textbf{AIESEC in Bengaluru}, Bengaluru \\
\textit{Senior Manager} \hfill Jun 2024 -- Feb 2025 \\
\begin{itemize}[leftmargin=*]
    \item Strengthened skills in cold outreach; organized meetings with prominent NGOs.
\end{itemize}
\textit{Junior Manager} \hfill Feb 2024 -- Jun 2024 \\
\begin{itemize}[leftmargin=*]
    \item Facilitated NGO partnerships aligned with UN SDGs through cold calling and research.
\end{itemize}

\textbf{Under25 Universe}, Bengaluru \\
\textit{Snapchat Opinion Leader} \hfill Jun 2023 -- Jan 2024 \\
\begin{itemize}[leftmargin=*]
    \item Created AR Snapchat lenses tailored to youth engagement and branding.
\end{itemize}

\section*{Skills \& Interests}
\textbf{Languages:} System Verilog, C, C++, Python, HTML/CSS, JavaScript, MATLAB \\
\textbf{Tools:} Cadence Virtuoso, Xilinx Vivado, LTSpice, Simulink, QUCS, KiCAD \\
\textbf{Interests:} Wildlife Photography, Violin (Intermediate)

\end{document}
